%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%% \usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{hyperref}
\hypersetup{%
  colorlinks=true,% hyperlinks will be black
  urlcolor=blue
}
\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Samim Pezeshki} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{Esfahan, Iran} % Your address
\moveleft.5\hoffset\centerline{psamim@gmail.com}
\moveleft.5\hoffset\centerline{(+98) 935 831 2099}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\section{OBJECTIVE}
Ability to operate as an effective team member and also team leader.
Proven ability to read, write and communicate in English fluently, properly and academically.
Worked with different remote teams  using different code-sharing tools,
version control systems, team organization techniques, online meetings and remote
planning sessions.
FOSS activist and advocate. Eager to learn and confront new challenges.
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION/ \\CERTIFICATES}

{\sl Bachelor of Science,} Civil Engineering 2009--2012 \\
{\sl Master of Science,} Software Engineering 2012--2017 \\
Concentration: Computer Science \\
Academic IELTS Grade 7
%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{SKILLS}

% {\sl Web:} \\
React front end development, with hooks! \\
Offline-first \\
Redux, GraphQL, CSS in JS, \\
Serverless technologies (Netlify, Lambda, Now) \\
NodeJS, \\
Different CMSs and frameworks (NextJS, Gatsby, Laravel, Wordpress), \\
LAMP stack (PHP, SQL, Linux, MySQL), \\
\\
Gitlab CI and other continuous integration/delivery tools, \\
Docker for development, deployment, automation and testing, \\
Bash/Zsh/Python for server automation, \\
Git, SVN and CVS. \\
Server management and configuration \\
\\
Embedded devices (Arduino, ARM, ESP) \\
MQTT, CoAP, \\
Qt and CPP for Raspberry Pi and Android devices, \\
Python programming for home automation on AppDaemon and HomeAssistant, \\
\\
Object-oriented and functional designs. \\
MVC and other design patterns, \\
Agile methodologies \\
\\
Java for desktop, Web and Android applications, \\
Ruby on Rails as back-end for mobile applications, \\
Apache Spark, R, MATLAB, Octave and Python for data processing, \\
Cassandra, Apache Pig, Mahout, Hadoop, Kafka \\
LibreCAD, LibreOffice, LaTeX and Emacs-lisp. \\
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Project Manager, Analyst, Frontend Engineer} \hfill 2018 \\
18Techs, DARKPOS  \\

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Design a complex multi-branded offline-first web and desktop application using
  React, Apollo GraphQL and material-ui
\item Implement and design complex business logics
\item Working and managing the project for a large fully-remote team
\item Connecting embedded devices to cloud services through modern APIs
\end{itemize}

{\sl Web Developer} \hfill 2017 \\
Fan Azma Gostar, Medical and Lab Equipment \\

\begin{itemize} \itemsep -2pt % Reduce space between items
\item UI interface design for embedded device (lab equipment) using Web
  technologies (React JS)
\item Protocol implementation for binary communication between the device and JS
  in browser
\item Working under highly constrained environment (low-level server APIs)
\end{itemize}

{\sl Embedded Device Developer} \hfill 2016 \\
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Implementing full home automation system using AppDaemon and HomeAssistant
\item Setting up centeral server on Raspberry Pi using Docker
\item Setting up variety of automation nodes on embedded devices communicating on MQTT
\end{itemize}

{\sl Embedded Device Developer} \hfill 2016 \\
Iran3D, 3D Printer Manufacturing \\

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Automation of software stack installation and bootstrapping 
\item UI interface design for embedded device (3D printer) using Qt framework
\end{itemize}

{\sl Android Developer} \hfill 2016 \\
ClickYab Advertising Agency

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Development of Clickyab advertising platform SDK for Android
\item Implementing VAST protocol
\item Overcoming SDK challenges such as complete stability, small size and support
  for all SDK versions
\end{itemize}

{\sl Android Developer} \hfill 2016 \\
Azmoona Educational Institute

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Development of Azmoona main Android application
\item CI and automated testing for Azmoona app
\end{itemize}

{\sl Mobile Developer and Automation Analyst} \hfill 2014 \\
Karapost International Postal Company

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Developed hand-held and PDA applications on Android platform and Windows CE for autmating different bussiness
  routines e.a. package pickups, deliveries and location tracking.
\item Developed and maintained the back-end cloud-based infrastructure needed for automating and information flow between
  hand-held devices and the main database server using REST-ful APIs and SOAP Web services.
\item Developed nation-wide monitoring platform for tracking and helping the
  decision making process inside the company considering customer relations and devices on hand.
\end{itemize}
 
{\sl Business Applications Developer}\hfill 2013 \\
Senior Developer at Jooyeshgar Inc.
\begin{itemize}
\item Designed CI tools and strategies for testing and deployment using Gitlab
  CI and Docker
\item Developed CRM software for business companies based on Web technologies as a back-end infrastructure.
\item Developed financial reporting platform for business companies based on Web
  technologies for using across end customers, managers and staff, from data entry
  to data warehouse.
\item Developed Web based accounting solutions for connecting nation-wide companies.
\end{itemize} 

{\sl Assistant Manager}\hfill 2012 \\
Tehran Elastic Co.
\begin{itemize}
\item Helped the company at management level in `High Technologies Department
  Building' in the University of Isfahan.
\end{itemize} 

{\sl Freelance Web Developer}\hfill 2011 \\
\begin{itemize}
\item Different Web-based solutions as student freelance projects on Ruby on Rails
  framework and deploying on Linux systems using PAAS technologies.
\item Developed Web applications using enterprise PHP frameworks.
\end{itemize} 

{\sl FOSS Community Related Works}\hfil \\
\begin{itemize}
\item Maintaining multiple AUR packages for ArchLinux
\item Development, publishing and maintenance of multiple hobby projects on Github for
  different GNU/Linux distributions
\end{itemize} 

%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%---------------------------------------------------------------------------------------- 

\section{COMMUNITY \\ ACTIVITIES}

Active member of {\it Isfahan Linux User Group} \\
Participant at {\it ZConf Open Source Community Conference} 2014, 2013 \\
Talk in Sheikh Bahai University on `First Hand Experiences in Open Education' \\
Talk in Sheikh Bahai University on `Firefox OS'. \\
Instructor at one-day Linux workshop in Esfahan University \\
Writer at `Salam Donya' magazine. \\
Member of organizer team at Software Freedom Day Festival, Isfahan 2014, 2013 \\
Talk at IsfahanLUG on `resize2fs' \\
Talk at IsfahanLUG on `org-mode' \\
Talk at IsfahanLUG on `Terminal Multiplexors' \\
Talk at IsfahanLUG on `Open Source Economics' \\
Talk at BIHE and essay on `Event-oriented Programming'

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{CONTACT \\ INFORMATION}
Email: \href{mailto:psamim@gmail.com}{psamim@gmail.com} \\
Skype: samim.pezeshki \\
Github: \href{http://github.com/psamim}{/\/psamim} \\
Homepage: \href{http://www.psam.im/}{psam.im} \\

\section{REFERENCES}
Available upon request.

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
